\section{Span and Linear independence}

\section{Bases}

% exercise 1

\begin{exercise}
Find all vector spaces that have exactly one basis.
\end{exercise}

\begin{proof}
	\par Consider all lines passing through origin.
\end{proof}

\begin{exercise}
\begin{enumerate}[(a)]
	\item Let $U$ be the subspace of $\mathbb{R}^5$ defined by
	      \[ U = {(x_1, x_2, x_3, x_4, x_5) \in \mathbb{R}^5 : x_1  = 3 x_2 \text{ and } x_3 = 7 x_4}\]
	      Find a basis of $U$.
	\item Extend the basis in part (a) to a basis of $\R^5$.
	\item Find a subspace $W$ of $\R^5$ such that \( \R^5 = U \oplus W\).
\end{enumerate}
\end{exercise}

\begin{proof}
	\begin{enumerate}[(a)]
		\item We can verify that \((3, 1, 0, 0, 0), ~ (0, 0, 7, 1, 0), ~ (0, 0, 0, 0, 1)\)
		      is a basis of $U$, and it spans U.
		      \\ Idea: We start from the basis of $\R^5$ and try to fit it into the given condition.

		\item \((3, 1, 0, 0, 0), ~ (0, 0, 7, 1, 0), ~ (0, 0, 0, 0, 1), ~ (0, 1, 0, 0, 0), ~ (0, 0, 1, 0, 0)\)
		      \\ Idea: Downgrade all vector to one dimensional (to obtain the basis of $\R^5$).

		\item \( \Span\{(0, 0, 0, 0, 1), ~ (0, 1, 0, 0, 0)\} \)
		      \\ Idea: Refer to the definition of direct sum.
	\end{enumerate}
\end{proof}

\begin{exercise}
Prove or disprove: there exists a basis \(p_0, p_1, p_2, p_3\) of \(\mathcal{P}_3 (\F)\)
such that none of the polynomials \(p_0, p_1, p_2, p_3\) has a degree 2.
\end{exercise}
\begin{proof}
	Consider
	\begin{align*}
		p_0 & = a_1               \\
		p_1 & = a_2 x             \\
		p_2 & = a_3 x^3           \\
		p_3 & = a_4 x^2 + a_5 x^3
	\end{align*}
	It is easy to verify that they are linearly independent, and span $\mathcal{P}_3(\F)$
\end{proof}

\begin{exercise}
Suppose \(v_{1}, v_{2}, v_{3}, v_{4}\) is a basis of $V$. Prove that \[
	v_{1} + v_{2}, v_{2} + v_{3}, v_{3} + v_{4}, v_{4}\]
is also a basis of $V$.
\end{exercise}
\begin{proof}
	We could obtain \(v_{1}, v_{2}, v_{3}\) with the following operation
	\begin{align}
		v_{3} + v_{4} - v_{4}                                     & = v_{3} \\
		v_{2} + v_{3} - (v_{3} + v_{4} - v_{4})                   & = v_{2} \\
		v_{1} + v_{2} - (v_{2} + v_{3} - (v_{3} + v_{4} - v_{4})) & = v_{1}
	\end{align}
	Which suggests that \(v_{1} + v_{2}, v_{2} + v_{3}, v_{3} + v_{4}, v_{4}\)
	also spans $V$. \\
	Next, we prove that they are linearly independent.

	\begin{align}
		  & a(v_{1} + v_{2} + b ( v_{2} + v_{3} ) + c (v_{3} + v_{4}) + d v_{4} \\
		= & a v_{1} + (a + b) v_{2} + (b + c) v_{3} + (c + d) v_{4}
	\end{align}
	Since \(v_{1}, v_{2}, v_{3}, v_{4}\) is a basis, we have \(a = b = c = d = 0\).
	This implies that \(v_{1} + v_{2}, v_{2} + v_{3}, v_{3} + v_{4}, v_{4}\)
	is also linearly independent.
\end{proof}

\begin{exercise}
Suppose $U$ and $W$ are subspaces of $V$ such that \(V = U \oplus W\).
Suppose also that \(u_{1},\dots,u_{m}\) is a basis of $U$ and \(w_{1},\dots,w_{n}\)
is a basis of $W$. Prove that \[u_{1},\dots,u_{m}, w_{1},\dots,w_{n}\]
is a basis of $V$.
\end{exercise}
\begin{proof}
	The linear independency of \(u_{1},\dots,u_{m}, w_{1},\dots,w_{n}\) is directly come from the definition of direct sum since \(U \cap W = {0}\).
	Since \(u_{1}, \dots, u_{m}\) is a basis of U. We can write any \(u \in U\) as a linear combination of \(u_{1}, \dots, u_{m}\). Similarly, we can write any \(w \in W\) as a linear combination of \(w_{1}, \dots, w_{n}\).
	Therefore, we can write any \(v \in V\) as a linear combination of \(u_{1}, \dots, u_{m}, w_{1}, \dots, w_{n}\).
\end{proof}
% End

\section{Dimension}

\begin{exercise}
Suppose $V$ is finite-dimensional and $U$ is a subspace of $V$ such that $ \dim U = \dim V$. Prove that $U = V$.
\end{exercise}

\begin{proof}
	Let \(u_1, \dots, u_n\) be a basis of $U$. Since $U$ is a subspace of $V$, we can extend the basis of $U$ to a basis of $V$.
	Since \( \dim U = \dim V\), every independent list of right length is also a base suggests that \(u_{1}, \dots, u_{n}\) also spans $V$. Therefore, \(U = V\).
\end{proof}

\begin{exercise}
Show that the subspaces of $\mathbb{R}^2$ are precisely the zero subspace, all lines in $\mathbb{R}^{2}$ through the origin, and $\R^2$ itself.
\end{exercise}
\begin{proof}
	\( \dim \mathbb{R}^{2} = 2 \implies \dim \text{subspaces of } \mathbb{R}^{2} \leq 2\)

	\begin{align}
		\text{When} \hspace{10pt} & \dim U = 0, & U = \{0\}.                               \\
		                          & \dim U = 1, & U \text{ is a line passing through origin.} \\
		                          & \dim U = 2, & U = \mathbb{R}^{2}.
	\end{align}



\end{proof}

% \begin{exercise}
% \begin{enumerate}[(a)]
% 	\item Let $U = {p \in P_{4}(\R) : p(6) = 0}$. Find a basis of $U$.
% 	\item Extend the basis in part (a) to a basis of $P_{4}(\R)$.
% 	\item Find a subspace $W$ of $P_{4}(\R)$ such that \(P_{4}(\R) = U \oplus W\).
% \end{enumerate}
% \end{exercise}
%
% \begin{proof}
% 	Proof
% \end{proof}

